Real-time resolution of short-read assembly graph using ONT long reads

### 2020-03-02 plos_latex_template.tex
plos

\documentclass[10pt,twocolumn,twoside]{genpaper}
\usepackage[numbers,sort&compress]{natbib}

\newcommand{\npscarf}{$\mathtt{npScarf}$}
\newcommand{\npscarfg}{$\mathtt{npScarf\_wag}$}
\newcommand{\npreader}{$\mathtt{npReader}$}
\newcommand{\npanalysis}{$\mathtt{npAnalysis}$}
\newcommand{\npbarcode}{$\mathtt{npBarcode}$}
\newcommand{\npgraph}{$\mathtt{npGraph}$}
\newcommand{\canu}{$\mathtt{Canu}$}
\newcommand{\unicycler}{$\mathtt{Unicycler}$}
\newcommand{\spades}{$\mathtt{SPAdes}$}
\newcommand{\hspades}{$\mathtt{hybridSPAdes}$}
\newcommand{\albacore}{$\mathtt{Albacore}$}
\newcommand{\racon}{$\mathtt{Racon}$}
\newcommand{\metrichor}{$\mathtt{Metrichor}$}
\newcommand{\minimap}{$\mathtt{minimap2}$}
\newcommand{\miniasm}{$\mathtt{miniasm}$}
\newcommand{\bwa}{$\mathtt{BWA\text{-}MEM}$}

@@

\usepackage{pdfpages} 
\usepackage{mathtools}
%\usepackage{play}
\usepackage{makeidx}
\usepackage{xcolor,colortbl}
\usepackage{longtable}
\usepackage{booktabs}
\usepackage{hyperref}
\usepackage{pdflscape}

\usepackage{amsmath,amsfonts,amssymb} % this is handy for mathematicians and physicists
			      % see http://www.ams.org/tex/amslatex.html

% \usepackage{showkeys} % this shows what labels you are using for cross
		      % references

\usepackage{graphicx} % standard graphics package for inclusion of
		      % images and eps files into LaTeX document

\usepackage{multirow}

\usepackage{float}
\usepackage[caption = false]{subfig}
% this code hacked from that of R Chandrasekhar from UWA
\newif\ifpdf
\ifx\pdfoutput\undefined
	\pdffalse    % we are not running pdfLaTeX
\else
	\pdfoutput=1 % we are running pdfLaTeX
	\pdftrue
\fi

\ifpdf
	\DeclareGraphicsExtensions{.pdf}  % this command defined in graphicx
	\pdfcompresslevel=9  % 0: no compression, 9: highest compression
			     % or, set compress_level 9 in file pdftex.cfg
\else
	\DeclareGraphicsExtensions{.ps}
\fi

\usepackage[linesnumbered,boxed,ruled,vlined]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}
% For code embedding (Bash, Java...)
\usepackage{listings}
\lstset{basicstyle=\ttfamily,
  showstringspaces=false,
  commentstyle=\color{red},
  keywordstyle=\color{blue}
}
\usepackage{latexsym}
\usepackage{mathtools}
\usepackage{amsmath}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

\usepackage{xr}
\externaldocument{supplementary}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%% Some functions provided  by the class

%Display line numbers on the margins
\lineno

%% use \onecolumn for onecolumn paper
\onecolumn

\title{
Real-time resolution of short-read assembly graph using ONT long reads}
\shorttitle{Real-time Graph Assembly}

%Authors
\author[1,$\ast$]{Son Hoang Nguyen}
\author[1]{Minh Duc Cao}
\author[1,2,3,4,$\ast$]{Lachlan Coin}

%Affiliation
\affil[1]{Institute for Molecular Bioscience, the University of Queensland, 
St Lucia, Brisbane, QLD 4072 Australia}
\correspondingauthor{
\textsuperscript{$\ast$}
To whom correspondence should be addressed. 
E-mails: l.coin@imb.uq.edu.au,s.hoangnguyen@imb.uq.edu.au
}

\affil[2]{
Department of Microbiology and Immunology, The University of Melbourne, Parkville, 3010, Australia}

\affil[3]{
Department of Clinical Pathology, The University of Melbourne, Parkville, 3010, Australia
}
\affil[4]{Department of Infectious Disease, Imperial College London, London, W2 1NY, UK
}

%Display ``This manuscript was compiled on XXXX''
\compiledate

%Set abstract (see below)
\abstract{
A streaming assembly pipeline utilising real-time Oxford Nanopore Technology (ONT) sequencing data is important for saving sequencing resources and reducing time-to-result. A previous approach implemented in  \npscarf{} provided an efficient streaming algorithm for hybrid assembly but was relatively prone to mis-assemblies compared to other graph-based methods. 
Here we present \npgraph{}, a streaming hybrid assembly tool using the assembly graph instead of the separated pre-assembly contigs. It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide. 
Application to synthetic and real data from bacterial isolate genomes show improved accuracy while still maintaining a low computational cost. 
%On top of that, we apply \npgraph{} on mock community in the very first application to improve metagenomics assembly in real-time with nanopore data. 
\npgraph{} also provides a graphical user interface (GUI) which provides a real-time visualisation of the progress of assembly.
 The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.
} 
%Set keywords
\keywords{hybrid assembly, assembly graph, real-time analysis, nanopore sequencing}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}
%Abstract and keywords have to be defined before \maketitle
\maketitle
\thispagestyle{fancy}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Introduction}

%Points:
% Sequencing is now easy and cheap. However time is still the bottlenect, especially for time critical applications

%One particular application is genome assembly

%Highlight the importance of real-time/hybrid assembly

%Gaps: Several tool apptemt to use long reads to

% \begin{itemize}
% \item The importance of having a real-time assembler for bacterial and small genomes: e.g. npscarf 
% \item The difficulty to resolve assembly graph in real-time.
% \item Available hybrid assembly methods using long reads: unicycler, ...
% \item an online algorithm to resolve assembly graph by long reads is needed, ...
% \item Requirements
%     \begin{itemize}
%     \item Support streaming: efficient with high yield (armortized analysis)
%     \item Statistically robust: online modification of the dynamic graph, back tracking edge deletion...
%     \item Standardisation : output GFA in real-time
%     \end{itemize}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section*{Results}
\subsection*{Resolving assembly graph in real-time}
\npgraph{} makes use of an assembly graph generated from assembling short reads using a de Bruijin
graph method such as \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$~\cite{Zerbino2008}
and $\mathtt{AbySS}$~\cite{Simpson2009}. The assembly graph consists of a list of contigs, and 
possible connections among these contigs. In building the assembly graph, the de Bruijin graph assembler attempts to extend 
each contig as far as possible, until there is more than one possible way of extending due to the repetitive sequences 
beyond the information contained in short reads. Hence each contig has multiple possible connections with others,
 creating knots in the assembly graph. \npgraph{}  uses the connectivity information from long reads to untangle these knots in real-time. 
 With sufficient data, when all the knots are removed, the assembly graph is simplified 
to a path which represents the complete assembly.

@@

%TODO: Because of the converting long reads to contig alignment to mapping to path, npgraph is faster than unicycler, and can be done in real-time

% 
% These local paths, given sufficient data, are expected to untangle the complicated graph and guide to the global Eulerian paths (or cycles if possible) that represent the entire genomic sequences. 
% \npgraph{} can be invoked and fully function from the command-line interface. In addition, in order to aid the visualization of the assembly process, a GUI has been developed as well.

\begin{figure}[!hpt]
\centering
\parbox{\textwidth}{
    \parbox{.57\textwidth}{
        \subfloat{\includegraphics[width=\hsize]{images/dashboard.png}}
    }
    \hskip1em
    \parbox{.44\textwidth}{%
        \subfloat{\includegraphics[width=\hsize]{images/graph-view.png}}
        \vskip1em
        \subfloat{\includegraphics[width=\hsize]{images/console-view.png}}  
    }
}
\caption[\npgraph{} user interface]{\npgraph{} user interface including Console (\textbf{0}) and GUI components (\textbf{1}-\textbf{6}). The GUI consists of the Dashboard (\textbf{1}-\textbf{5}) and the Graph View (\textbf{6}). From the Dashboard there are 5 components as follow: \textbf{1} the assembly graph input field; \textbf{2} the long reads input field; \textbf{3} the aligner settings field; \textbf{4} control buttons (start/stop) to monitor the real-time scaffolding process; \textbf{5} the statistics plots for the assembly result.}
\label{figure:npgraph_gui}
\end{figure}

We also provide a Graphical User Interface (GUI) for \npgraph{}. The GUI includes the dashboard for controlling the settings of the program and a window for visualization of the assembly graph 
in real-time (Figure~\ref{figure:npgraph_gui}). 
In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. The practice is to support the real-time monitoring of
the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.

% TODO: Extract information from here to caption
% The box numbered \textbf{1} on Figure~\ref{figure:npgraph_gui} is designed for this task.
% Only after an assembly graph is loaded successfully, users can move to box \textbf{2} to specify the nanopore input data.
% Settings for an aligner (\bwa{} or \minimap{}) in box \textbf{3} is required if the input is the raw sequences in FASTA/FASTQ format. Another option is to run the alignment independently and provide SAM/BAM input for the next stage of bridging and assembly. This stage is controlled by buttons in box \textbf{4}: the START button ignites the process while the STOP button can prematurely terminate it and output the assembly result till that moment. The plots from the right panel (\textbf{5}) depicts real-time statistics of the assembly contigs inferred from the graph.
% From the second window (\textbf{6}), the colored vertices imply unique contigs while the white ones involve either unspecified or repetitive elements. The number of different colors (other than white) indicates the amount of abundant groups being detected as population bins (\EG{} chromosome versus different plasmids, or different bins in metagenomics).

\subsection*{Evaluation using synthetic data}
To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 %%COMMENT_LC - why just indicate unicyler version and not others? 
using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~\cite{Mikheenko2018quast5}.

\LTcapwidth=\linewidth
% \footnotesize
\begin{longtable}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
\caption[Comparison of assemblies using \npgraph{} and other methods on 5 synthetic data sets]{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on representative \unicycler{}`s synthetic data downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} \label{table:npgraph_compare} \\

 \toprule
    &       & \cthead{1}{Assembly} &     & 
    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
    \cthead{3}{Run times} \\
    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
    \cthead{3}{(CPU hrs)} \\
\toprule    
\endfirsthead

\multicolumn{10}{c}%
{{\tablename\ \thetable{} -- continued from previous page}} \\
 \toprule
    &       & \cthead{1}{Assembly} &     & 
    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
    \cthead{3}{Run times} \\
    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
    \cthead{3}{(CPU hrs)} \\
\toprule    
\endhead

\hline \multicolumn{10}{|r|}{{Continued on next page}} \\ \hline
\endfoot

\hline \hline
\endlastfoot

@@

\end{longtable}

@@

Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
%FOLLOWING REPEATS WHAT YOU SAID BEFORE
%In the first column of applied methods, beside \unicycler{} and $\mathtt{hybridSPAdes}$, the preceding real-time scaffolder \npscarf{} was included as well.
%On the other hand, 2 settings to run \npgraph{} were studied to have insights into the effect of using different alignment methods on its result.

>>>>

% Template for PLoS
% Version 3.5 March 2018
%
% % % % % % % % % % % % % % % % % % % % % %
%
% -- IMPORTANT NOTE
%
% This template contains comments intended 
% to minimize problems and delays during our production 
% process. Please follow the template instructions
% whenever possible.
%
% % % % % % % % % % % % % % % % % % % % % % % 
%
% Once your paper is accepted for publication, 
% PLEASE REMOVE ALL TRACKED CHANGES in this file 
% and leave only the final text of your manuscript. 
% PLOS recommends the use of latexdiff to track changes during review, as this will help to maintain a clean tex file.
% Visit https://www.ctan.org/pkg/latexdiff?lang=en for info or contact us at latex@plos.org.
%
%
% There are no restrictions on package use within the LaTeX files except that 
% no packages listed in the template may be deleted.
%
% Please do not include colors or graphics in the text.
%
% The manuscript LaTeX source should be contained within a single file (do not use \input, \externaldocument, or similar commands).
%
% % % % % % % % % % % % % % % % % % % % % % %
%
% -- FIGURES AND TABLES
%
% Please include tables/figure captions directly after the paragraph where they are first cited in the text.
%
% DO NOT INCLUDE GRAPHICS IN YOUR MANUSCRIPT
% - Figures should be uploaded separately from your manuscript file. 
% - Figures generated using LaTeX should be extracted and removed from the PDF before submission. 
% - Figures containing multiple panels/subfigures must be combined into one image file before submission.
% For figure citations, please use "Fig" instead of "Figure".
% See http://journals.plos.org/plosone/s/figures for PLOS figure guidelines.
%
% Tables should be cell-based and may not contain:
% - spacing/line breaks within cells to alter layout or alignment
% - do not nest tabular environments (no tabular environments within tabular environments)
% - no graphics or colored text (cell background color/shading OK)
% See http://journals.plos.org/plosone/s/tables for table guidelines.
%
% For tables that exceed the width of the text column, use the adjustwidth environment as illustrated in the example table in text below.
%
% % % % % % % % % % % % % % % % % % % % % % % %
%
% -- EQUATIONS, MATH SYMBOLS, SUBSCRIPTS, AND SUPERSCRIPTS
%
% IMPORTANT
% Below are a few tips to help format your equations and other special characters according to our specifications. For more tips to help reduce the possibility of formatting errors during conversion, please see our LaTeX guidelines at http://journals.plos.org/plosone/s/latex
%
% For inline equations, please be sure to include all portions of an equation in the math environment.  For example, x$^2$ is incorrect; this should be formatted as $x^2$ (or $\mathrm{x}^2$ if the romanized font is desired).
%
% Do not include text that is not math in the math environment. For example, CO2 should be written as CO\textsubscript{2} instead of CO$_2$.
%
% Please add line breaks to long display equations when possible in order to fit size of the column. 
%
% For inline equations, please do not include punctuation (commas, etc) within the math environment unless this is part of the equation.
%
% When adding superscript or subscripts outside of brackets/braces, please group using {}.  For example, change "[U(D,E,\gamma)]^2" to "{[U(D,E,\gamma)]}^2". 
%
% Do not use \cal for caligraphic font.  Instead, use \mathcal{}
%
% % % % % % % % % % % % % % % % % % % % % % % % 
%
% Please contact latex@plos.org with any questions.
%
% % % % % % % % % % % % % % % % % % % % % % % %

\documentclass[10pt,letterpaper]{article}
\usepackage[top=0.85in,left=2.75in,footskip=0.75in]{geometry}

% amsmath and amssymb packages, useful for mathematical formulas and symbols
\usepackage{amsmath,amssymb}

% Use adjustwidth environment to exceed column width (see example table in text)
\usepackage{changepage}

% Use Unicode characters when possible
\usepackage[utf8x]{inputenc}

% textcomp package and marvosym package for additional characters
\usepackage{textcomp,marvosym}

% cite package, to clean up citations in the main text. Do not remove.
\usepackage{cite}

% Use nameref to cite supporting information files (see Supporting Information section for more info)
\usepackage{nameref,hyperref}

% line numbers
\usepackage[right]{lineno}

% ligatures disabled
\usepackage{microtype}
\DisableLigatures[f]{encoding = *, family = * }

% color can be used to apply background shading to table cells only
\usepackage[table]{xcolor}

% array package and thick rules for tables
\usepackage{array}

% create "+" rule type for thick vertical lines
\newcolumntype{+}{!{\vrule width 2pt}}

% create \thickcline for thick horizontal lines of variable length
\newlength\savedwidth
\newcommand\thickcline[1]{%
  \noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
  \cline{#1}%
  \noalign{\vskip\arrayrulewidth}%
  \noalign{\global\arrayrulewidth\savedwidth}%
}

% \thickhline command for thick horizontal lines that span the table
\newcommand\thickhline{\noalign{\global\savedwidth\arrayrulewidth\global\arrayrulewidth 2pt}%
\hline
\noalign{\global\arrayrulewidth\savedwidth}}

% Remove comment for double spacing
%\usepackage{setspace} 
%\doublespacing

% Text layout
\raggedright
\setlength{\parindent}{0.5cm}
\textwidth 5.25in 
\textheight 8.75in

% Bold the 'Figure #' in the caption and separate it from the title/caption with a period
% Captions will be left justified
\usepackage[aboveskip=1pt,labelfont=bf,labelsep=period,justification=raggedright,singlelinecheck=off]{caption}
\renewcommand{\figurename}{Fig}

% Use the PLoS provided BiBTeX style
\bibliographystyle{plos2015}

% Remove brackets from numbering in List of References
\makeatletter
\renewcommand{\@biblabel}[1]{\quad#1.}
\makeatother

% Header and Footer with logo
\usepackage{lastpage,fancyhdr,graphicx}
\usepackage{epstopdf}
%\pagestyle{myheadings}
\pagestyle{fancy}
\fancyhf{}
%\setlength{\headheight}{27.023pt}
%\lhead{\includegraphics[width=2.0in]{PLOS-submission.eps}}
\rfoot{\thepage/\pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrule}{\hrule height 2pt \vspace{2mm}}
\fancyheadoffset[L]{2.25in}
\fancyfootoffset[L]{2.25in}
\lfoot{\today}

%% Include all macros below

\newcommand{\lorem}{{\bf LOREM}}
\newcommand{\ipsum}{{\bf IPSUM}}

%% END MACROS SECTION

%% npGraph
\newcommand{\npscarf}{$\mathtt{npScarf}$}
\newcommand{\npscarfg}{$\mathtt{npScarf\_wag}$}
\newcommand{\npreader}{$\mathtt{npReader}$}
\newcommand{\npanalysis}{$\mathtt{npAnalysis}$}
\newcommand{\npbarcode}{$\mathtt{npBarcode}$}
\newcommand{\npgraph}{$\mathtt{npGraph}$}
\newcommand{\canu}{$\mathtt{Canu}$}
\newcommand{\unicycler}{$\mathtt{Unicycler}$}
\newcommand{\spades}{$\mathtt{SPAdes}$}
\newcommand{\hspades}{$\mathtt{hybridSPAdes}$}
\newcommand{\albacore}{$\mathtt{Albacore}$}
\newcommand{\racon}{$\mathtt{Racon}$}
\newcommand{\metrichor}{$\mathtt{Metrichor}$}
\newcommand{\minimap}{$\mathtt{minimap2}$}
\newcommand{\miniasm}{$\mathtt{miniasm}$}
\newcommand{\bwa}{$\mathtt{BWA\text{-}MEM}$}

@@

\usepackage{multirow} 
\usepackage{float}
\usepackage[caption = false]{subfig}

\usepackage[linesnumbered,boxed,ruled,vlined]{algorithm2e}
\newcommand\mycommfont[1]{\footnotesize\ttfamily\textcolor{blue}{#1}}
\SetCommentSty{mycommfont}
% For code embedding (Bash, Java...)
\usepackage{listings}
\lstset{basicstyle=\ttfamily,
  showstringspaces=false,
  commentstyle=\color{red},
  keywordstyle=\color{blue}
}
\usepackage{latexsym}
\usepackage{mathtools}
\DeclareMathOperator*{\argmax}{argmax}
\DeclareMathOperator*{\argmin}{argmin}

\usepackage{longtable,booktabs}
%% End preloads

\begin{document}
\vspace*{0.2in}

% Title must be 250 characters or less.
\begin{flushleft}
{\Large
\textbf\newline{Real-time resolution of short-read assembly graph using ONT long reads} % Please use "sentence case" for title and headings (capitalize only the first word in a title (or heading), the first word in a subtitle (or subheading), and any proper nouns).
}
\newline
% Insert author names, affiliations and corresponding author email (do not include titles, positions, or degrees).
\\
Son Hoang Nguyen\textsuperscript{1*},
Minh Duc Cao\textsuperscript{1},
Lachlan Coin\textsuperscript{1,2,3,4*}
\\
\bigskip
\textbf{1} Institute for Molecular Bioscience, the University of Queensland, 
St Lucia, Brisbane, QLD 4072 Australia
\\
\textbf{2} Department of Microbiology and Immunology, The University of Melbourne, Parkville, 3010, Australia
\\
\textbf{3} Department of Clinical Pathology, The University of Melbourne, Parkville, 3010, Australia
\\
\textbf{4} Department of Infectious Disease, Imperial College London, London, W2 1NY, UK
\bigskip

% Use the asterisk to denote corresponding authorship and provide email address in note below.
*s.hoangnguyen@imb.uq.edu.au,l.coin@imb.uq.edu.au

\end{flushleft}
% Please keep the abstract below 300 words
\section*{Abstract}
A streaming assembly pipeline utilising real-time Oxford Nanopore Technology (ONT) sequencing data is important for saving sequencing resources and reducing time-to-result. A previous approach implemented in  \npscarf{} provided an efficient streaming algorithm for hybrid assembly but was relatively prone to mis-assemblies compared to other graph-based methods. 
Here we present \npgraph{}, a streaming hybrid assembly tool using the assembly graph instead of the separated pre-assembly contigs. It is able to produce more complete genome assembly by resolving the path finding problem on the assembly graph using long reads as the traversing guide. 
Application to synthetic and real data from bacterial isolate genomes show improved accuracy while still maintaining a low computational cost. 
%On top of that, we apply \npgraph{} on mock community in the very first application to improve metagenomics assembly in real-time with nanopore data. 
\npgraph{} also provides a graphical user interface (GUI) which provides a real-time visualisation of the progress of assembly.
 The tool and source code is available at \url{https://github.com/hsnguyen/assembly}.

% Please keep the Author Summary between 150 and 200 words
% Use first person. PLOS ONE authors please skip this step. 
% Author Summary not valid for PLOS ONE submissions.   
\section*{Author summary}

\linenumbers

% Use "Eq" instead of "Equation" for equation citations.
\section*{Introduction}

@@

\section*{Materials and methods}
\subsection*{Application overview}
\npgraph{} makes use of an assembly graph generated from assembling short reads using a de Bruijin
graph method such as \spades{}~\cite{BankevichNA2012}, $\mathtt{Velvet}$~\cite{Zerbino2008}
and $\mathtt{AbySS}$~\cite{Simpson2009}. The assembly graph consists of a list of contigs, and 
possible connections among these contigs. In building the assembly graph, the de Bruijin graph assembler attempts to extend 
each contig as far as possible, until there is more than one possible way of extending due to the repetitive sequences 
beyond the information contained in short reads. Hence each contig has multiple possible connections with others,
 creating knots in the assembly graph. \npgraph{}  uses the connectivity information from long reads to untangle these knots in real-time. 
 With sufficient data, when all the knots are removed, the assembly graph is simplified 
to a path which represents the complete assembly.

@@

We also provide a Graphical User Interface (GUI) for \npgraph{}. The GUI includes the dashboard for controlling the settings of the program and a window for visualization of the assembly graph 
in real-time (Figure~\ref{figure:npgraph_gui}). 
In this interface, the assembly graph loading stage is separated from the actual assembly process so that users can check for the graph quality first before carry out any further tasks.
A proper combination of command line and GUI can provide an useful streaming pipeline that copes well with MinION output data. The practice is to support the real-time monitoring of
the results from real-time sequencing~\cite{CaoGC2016,Cao2017scaffolding,Nguyen2017barcode} that allow the analysis to take place abreast to a nanopore sequencing run.
\begin{figure}[!hpt]
\centering
\parbox{\textwidth}{
    \parbox{.57\textwidth}{
        \subfloat{\includegraphics[width=\hsize]{images/dashboard.png}}
    }
    \hskip1em
    \parbox{.44\textwidth}{%
        \subfloat{\includegraphics[width=\hsize]{images/graph-view.png}}
        \vskip1em
        \subfloat{\includegraphics[width=\hsize]{images/console-view.png}}  
    }
}
\caption[\npgraph{} user interface]{\npgraph{} user interface including Console (\textbf{0}) and GUI components (\textbf{1}-\textbf{6}). The GUI consists of the Dashboard (\textbf{1}-\textbf{5}) and the Graph View (\textbf{6}). From the Dashboard there are 5 components as follow: \textbf{1} the assembly graph input field; \textbf{2} the long reads input field; \textbf{3} the aligner settings field; \textbf{4} control buttons (start/stop) to monitor the real-time scaffolding process; \textbf{5} the statistics plots for the assembly result.}
\label{figure:npgraph_gui}
\end{figure}

\subsection*{Algorithm in details}
The work flow of \npgraph{} mainly consists of 3 stages: (1) assembly graph pre-processing; (2) graph resolving and simplifying; (3) post-processing and reporting results. 
The first step is to load the assembly graph of Illumina contigs and analyze its components' property, including binning and multiplicity estimation.
The second step works on the processed graph and the long read data that can be provided in real-time by ONT sequencer. Based on the paths induced from long reads, the assembly graph will be resolved on-the-fly.
Finally, the graph is subjected to the last attempt of resolving and cleaning, as well as output the final results. The whole process can be managed by using either command-line interface or GUI.
Among three phases, only the first one must be performed prior to the MinION sequencing process in a streaming setup.
The algorithm works on the assembly graph of Illumina contigs, so the terms \emph{contigs} and \emph{nodes} if not mentioned specifically, would be used interchangeable throughout this context.
\subsubsection*{Contigs binning}
Contigs should belong to single or multiple groups, or \emph{bins}, that would represent different assembly units, \EG{} chromosome , plasmids, of different species if applying to a metagenomics dataset. 
A binning step is needed to assign membership of each contig to its corresponding group.

% After identifying the bins, we implemented a graph traversal to assign more unique nodes to them, given the graph topology as well as statistics calculated by length and coverage of each contigs. 
Independent from the contigs clustering in the pre-processing step, additional evidence of nodes' uniqueness can be acquired using the long reads during the assembly process. Given enough data, the multiplicity of an ambiguous node can be determined based on the set of all bridges rooted from itself.
On the other hand, external binning tools such as MetaBAT~\cite{Kang2015metabat}, maxbin~\cite{Wu2014maxbin} can be employed in \npgraph{} as well.
%If external binning algorithm is employed, the resulting output must be converted into a text file that specifies the corresponding bin of every contigs, just like output from MetaBAT. By that, each line of the file would be:
%$
%\mathtt{<contig\_ID>} \; ~ \mathtt{<bin\_ID>}
%$
%where $\mathtt{bin\_ID}=0$ indicates unspecified binned contigs.
\subsubsection*{Multiplicity estimation}
Now bins of the main unique contigs had been identified, however, they only make up a certain proportion of the contigs set. From here, we need to assign bin membership and multiplicity for all other nodes of the graph, especially the repetitive ones. To do so, we relied on the graph's topology and the estimated read coverage of initial contigs from SPAdes.
Given all contigs' coverage values as nodes' weight, we need to estimate those of edges and in return, using them to re-estimate the coverage for repetitive nodes if necessary. After this process, we will have a graph with optimized weighted components that would suggest their multiplicities more exactly. Basically the computation is described as in following steps:

%\subsection*{Untangling assembly graph by stream of nanopore data.}
\subsubsection*{Building bridges in real-time}
Bridge is the data structure designed for tracking the possible connections between two anchored nodes (of unique contigs) in the assembly graph.
A bridge must start from a unique contig, or \emph{anchor} node, and end at another when completed. Located in-between are nodes known as \emph{steps} and distances between them are called \emph{spans} of the bridge. Stepping nodes are normally repetitive contigs and indicative for a path finding operation later on. In a complicated assembly graph, the more details the bridge, \emph{a.k.a.} more steps in-between, the faster and more accurate the linking path it would resolve. A bridge's function is complete when it successfully return the ultimate linking path between 2 anchors.

\subsubsection*{Path finding algorithm}
Given a bridge with 2 anchors, a path finding algorithm is invoked to find all candidate paths between them. Each of these paths is given a score of alignment-based likelihood which are updated immediately as long as there is an appropriate long read being generated by the sequencer. As more nanopore data arrives, the divergence between candidates' score becomes greater and only the top-scored ones are kept for the next round.
We implement a modified stack-based version utilizing Dijkstra's shortest path finding algorithm~\cite{Dijkstra1959} to reduce the search space when using Depth-First Search.

In many cases, due to dead-ends, there not always exist a path in the assembly graph connecting two anchors as suggested by the alignments. In this case, if enough long reads coverage (20X) are met, a consensus module is invoked and the resulting sequence is contained in a \emph{pseudo} edge.
\subsubsection*{Graph simplification in real-time}
\npgraph{} resolves the graph by reducing its complexity perpetually using the long reads that can be streamed in real-time.
Whenever a bridge is finished (with a unique linking path), the assembly graph is \emph{transformed} or \emph{reduced} by replacing its unique path with a composite edge and removing any unique edges (edges coming from unique nodes) along the path. The assembly graph would have at least one edge less than the original after the reduction. The nodes located on the reduced path, other than 2 ends, also have their multiplicities subtracted by one and the bridge is marked as finally resolved without any further modifications.

Figure~\ref{figure:npgraph_graphview} presents an example of the results before and after graph resolving process in the GUI.
The result graph, after cleaning, would only report the significant connected components that represents the final contigs.
Smaller fragments, even unfinished but with high remaining coverage, are also presented as potential candidates for further downstream analysis.
Further annotation utility can be implemented in the future better monitoring the features of interests as in \npscarf{}.
\subsubsection*{Result extraction and output}
\npgraph{} reports assembly result in real-time by decomposing the assembly graph into a set of longest straight paths (LSP), each of the LSP will spell a contig in the assembly report.
The final assembly output contains files in both FASTA and GFAv1 format (\url{https://github.com/GFA-spec/GFA-spec}). While the former only retains the actual genome sequences from the final decomposed graph, the latter output file can store almost every properties of the ultimate graph such as nodes, links and potential paths between them.

% Results and Discussion can be combined.
\section*{Results}
\subsection*{Evaluation using synthetic data}
To evaluate the performance of the method, \npgraph{} 1.1 was tested along with \spades{}, \spades{} hybrid from version 3.13.1, ~\cite{AntipovKM2015}, \npscarf{} (japsa 1.7-02), and \unicycler{} version 0.4.6 %%COMMENT_LC - why just indicate unicyler version and not others? 
using \unicycler{}`s synthetic data set~ \cite{Wick2017unicycler} . 
The data set is a simulation of Illumina and MinION raw data, generated \emph{in silico} based on available microbial references.
We ran hybrid assembly methods using the entire nanopore data and the reciprocal results were evaluated by QUAST 5.0.2~\cite{Mikheenko2018quast5}.

\begin{table}[!ht]
\begin{adjustwidth}{-2.25in}{0in} % Comment out/remove adjustwidth environment if table fits in text column.
\centering
\caption{Comparison of assemblies produced in batch-mode using \npgraph{} and other hybrid assembly methods on representative \unicycler{}`s synthetic data downloaded from \url{https://cloudstor.aarnet.edu.au/plus/index.php/s/dzRCaxLjpGpfKYW}} 
\label{table:npgraph_compare}
\begin{tabular}{llcrrrrr@{\hspace{2pt}}c@{\hspace{2pt}}r}
 \hline
    &       & \cthead{1}{Assembly} &     & 
    \cthead{1}{N50}  & \cthead{1}{Mis-} &  \cthead{1}{Error}  &
    \cthead{3}{Run times} \\
    & \cthead{1}{Method} & \cthead{1}{size (Mbp)} & \cthead{1}{\#Contigs} &
    \cthead{1}{(Kbp)} & \cthead{1}{assemblies} & \cthead{1}{(per 100 Kbp)} &  
    \cthead{3}{(CPU hrs)} \\
\thickhline

@@

\end{tabular}
\end{adjustwidth}
\end{table}

@@

Table~\ref{table:npgraph_compare} shows comparative results running different methods on 5 synthetic data sets, simulated from complete genomes of \emph{Mycobacterium~tuberculosis} H37Rv, \emph{Klebsiella~pneumoniae} 30660/NJST258\_1, \emph{Saccharomyces~cerevisiae} S288c, \emph{Shigella~sonnei} 53G and \emph{Shigella~dysenteriae} Sd197.
